Single Cell Xenopus TMT Analysis

### 2020-03-06 Manuscript/Manuscript.Rmd
updated

library(knitr)
library(tidyverse)
library(RColorBrewer)
#library(pheatmap)
library(ComplexHeatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)
library(cowplot)
library(patchwork)
source("../functions.R")
library(knitcitations)
library(ggplotify)

@@

@@

>>>>

library(knitr)
library(tidyverse)
library(RColorBrewer)
#library(pheatmap)
library(ComplexHeatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)
library(cowplot)
library(patchwork)
source("../functions.R")
library(knitcitations)
library(ggplotify)
library(latex2exp)

@@

$$var\left(\sum_{i=1}^n X_{i}\right) = \sum_{i=1}^{n} var(X_{i}) + 2\sum_{i,j:i<j}^{n} cov(X_{i},X_{j})$$

$$\sigma_{{}_{total}} = \sum_{i=1}^{n} \sigma_{X_{i}}^2 + 2\sum_{i,j:i<j}^{n} \rho(X_{i},X_{j})\sigma_{X_i}\sigma_{X_j}$$

@@

$$
R =
\begin{bmatrix} 
\rho_{11} & \rho_{12} & \cdots & \rho_{1p} \\
\rho_{21} & \rho_{22} & \cdots & \rho_{2p} \\
\vdots & \vdots & \ddots & \vdots \\
\rho_{p1} & \rho_{p2} & \cdots & \rho_{pp}
\end{bmatrix}
$$

```{r}
library(magick)

cowplot::ggdraw() + cowplot::draw_image(magick::image_read_pdf("../images/preview.pdf", density = 600))

$$
\begin{bmatrix}
\sigma(X_{1}) \\
\sigma(X_{1}) \\
\sigma(X_{1}) \\
\vdots \\
\sigma(X_{i}) \\
\end{bmatrix}^2
+
\begin{bmatrix} 
\rho(X_1,X_2) \\
\rho(X_1,X_3) \\
\rho(X_1,X_4) \\
\vdots \\
\rho(X_i,X_j)
\end{bmatrix}

\begin{bmatrix}
\sigma(X_{1}) \\
\sigma(X_{1}) \\
\sigma(X_{1}) \\
\vdots \\
\sigma(X_{i}) \\
\end{bmatrix}

\begin{bmatrix}
\sigma(X_{2}) \\
\sigma(X_{3}) \\
\sigma(X_{4}) \\
\vdots \\
\sigma(X_{j}) \\
\end{bmatrix}
 $$

### 2020-03-06 Untitled.Rmd
updated

ggplot(allKEGG, aes(x = corSkew, y = medCV)) + geom_point(aes(color = interval)) +
  geom_label_repel(data = allKEGG, 
                  aes(label = KEGG_name), 
                  colour = 'black', 
                  size = 2,
                  force = 10)

@@

p1/p2 + 
  plot_annotation(title = "Glycolysis",
                  tag_levels = "A") +
  plot_layout(heights = c(2,1))

# pathview(genes, 
#          pathway.id = pathway, 
#          species = 'mmu', 
#          same.layer = F,
#          low = list(gene = 'blue'),
#          mid = list(gene = 'transparent'),
#          high = list(gene = 'red'),
#          limit = list(gene = c(-2,2))
# )
  p1
```

>>>>

ggplot(allKEGG, aes(x = medCors, y = medCV)) + geom_point(aes(color = interval)) +
  geom_label_repel(data = allKEGG, 
                  aes(label = KEGG_name), 
                  colour = 'black', 
                  size = 2,
                  force = 10)

@@

p1/p2 + 
  plot_annotation(tag_levels = "A") +
  plot_layout(heights = c(2,1))

# pathview(genes, 
#          pathway.id = pathway, 
#          species = 'mmu', 
#          same.layer = F,
#          low = list(gene = 'blue'),
#          mid = list(gene = 'transparent'),
#          high = list(gene = 'red'),
#          limit = list(gene = c(-2,2))
# )
```
